\begin{frame}{Characteristics of the Ideal Research Topic}
  %The characteristics of an ideal topic are to some extent incompatible:}%
  \begin{itemize}
    \only<1>{
      \item
        \textbf{The subject should be timely.}
        %
        Previous groundwork should leave your research problem ripe for completion,
        and it should be in an active area with potential for future work and
        employment.\\\vspace{2em}%
              
        On the other hand, if a field is too crowded, and the subject too prominent,
        then you risk being `scooped' by a more experienced researcher who is
        able to work faster than you. In this case, you may be forced to start over
        again (rather disastrous) or at least publish jointly (possibly a blessing,
        but surely an inconvenience).%
    } 
    \only<2>{
      \item
        \textbf{Your work should lead to a well-defined set 
        of results to which you can lay claim.}
        %
        In particular, career prospects will be lessoned if you merely
        contribute a small piece of a very large project, a piece of software which
        is closely identified with a project, or is published with a long list of
        collaborators.\\\vspace{2em}%
    
        On the other hand, it is impossible to work in a vacuum, and your task
        can be significantly harder if you don't have a group of people working on
        closely related problems with whom you can interact and share code.%
    } 
    \only<3>{
      \item%
        \textbf{The best topics show a high level of
        creativity -- and are often somewhat speculative.}
        %
        It is often unclear at first how the ideas will develop.\\\vspace{2em}%
      
        On the other hand, a multiyear plan of research is a very valuable asset.%
    }
    \only<4>{
      \item
        \textbf{You should really enjoy the subject, and want to
        spend the next several weeks/months/years with it!}
        \\\vspace{2em}%
      
        On the other hand, an ideal subject in a foreign subject is of no use without
        someone\(s\) who is willing to direct you in it.%
    }
  \end{itemize}

  \only<4>{%
      \vspace{3cm}\centering{\textit{Clearly some compromise is necessary here!}}%
  }%
\end{frame}
